The regularity of ODEs and thimble integrals \\ with respect to Borel summation \begin{draft}\textbf{[DRAFT]}\end{draft}

### 2024-09-09 borel-regularity.tex
Make notes during meeting

Once we know $\iota_a$, we can go through the steps of the Borel regularization process and show that we end up with the same function we started with.
\begin{theorem}[also \ref{thm:maxim-proof}]\label{thm:maxim}
If the integral defining $I_a$ is absolutely convergent, then $I_a$ is Borel regular. More explicitly:
\begin{enumerate}
\item\label{part-1} The function $I_a$ has an asymptotic expansion $\series{I}_a \defeq \aexp^\theta I_a$, which lies in the space $e^{-z \alpha} z^{-1/2} \C\llbracket z^{-1}\rrbracket$. Here, $\theta$ is the direction of the ray $\mathcal{J}^\theta_{\zeta, \alpha}$ that defines the thimble.
\item\label{part-2} The Borel transform $\series{\iota}_a \defeq \borel_\zeta \series{I}_a$ converges near $\zeta = \alpha$.
\item\label{part-3} The sum of $\series{\iota}_a$ can be analytically continued along the ray $\mathcal{J}_{\zeta, \alpha}^\theta$. Its Laplace transform along that ray is well-defined, and equal to $I_a$.
\end{enumerate}
\end{theorem}
\begin{draft}
This result confirms the expectations that thimble integrals are equal to the Borel resummation of its asymptotics~\cite[Section~2]{dunne-unsal}. Although the same result is conjectured to hold in higher dimensions, our proof might not straighfowardly generalize, hence we leave the discussion to future works.

Notice also that an alternative proof can be done using Nevanlinna's theorem~\cite{nevanlinna}, but it will require an accurate control of the asymptotics of $I_a$, which should be uniform and 1-Gevrey in a large enough sector. Instead, our approach avoids the analysis of the asymptotics by working in the position domain. In fact, we use that $I_a$ can be regarded as a Laplace trasnform.  
\end{draft}
\begin{revised}
For one-dimensional thimbles, this result confirms the expectation that evaluating a thimble integral should be equivalent to taking the Borel sum of its asymptotic series~\cite[Section~2]{dunne-unsal}. Confirming this expectation in higher dimensions would be an interesting topic for future work, since our argument may not generalize straightforwardly.

As an alternative to our argument, Theorem~\ref{thm:maxim} could be deduced from Nevanlinna's theorem~\cite{nevanlinna}. However, that would require a careful asymptotic analysis of $I_a$: one would have to show that its asymptotic series is $1$-Gevrey and uniformly asymptotic to it on a large enough sector. We avoid this asymptotic analysis by working in the position domain and recasting $I_a$ as a Laplace transform integral.
\end{revised}
%
\subsubsection{Other results}\label{sec:other_results}
%
\paragraph{New perspectives on the Laplace transform}
%
For Borel summation to work as described in Theorems~\ref{thm:soln_is_Borel_sum} and~\ref{thm:maxim}, one usually needs to take the Laplace and Borel transforms using a particular position coordinate and integration base point. To explain this aspect of Borel regularity, we introduce a geometric picture of the Laplace and Borel transforms, generalizing the position domain from the complex plane to a translation surface $B$. Each translation chart $\zeta$ gives a different version of the Laplace transform, whose associated frequency domain is the cotangent space $T^*_{\zeta = 0} B$. The frequency coordinate $z$ is a canonical coordinate on $T^*_{\zeta = 0}B$, or on $T^*_{\zeta = 0}B^{\otimes n}$ if $\zeta = 0$ is a singularity with cone angle $2\pi n$. The details of this picture are discussed in Sections \ref{sec:geometry_laplace} and \ref{sec:geometry_borel}.
\begin{center}
\phaseSpaceLaplace
\captionof{figure}{The frequency coordinate $z$ on the cotangent spaces of an ordinary point and a singular point. The singularity shown here has cone angle $6\pi$, like the singularities of the translation surface associated with the Airy function.}
\end{center}

@@

In the literature on Borel summation, the Airy equation has been discussed many times, using different approaches and conventions. In Section~\ref{airy-comparison}, we explain how the treatments in \cite[Section 2.2]{lectures-Marino}, \cite[Section 6.14]{diverg-resurg-i}, and \cite[Section 2.2]{kawai-takei} line up with ours.
 \begin{todo}Other treatments of the anharmonic oscillator: \cite{bender-wu}\cite[Appendix B]{aniceto2019primer}\cite[Section 2.5.3]{sternin1995borel}).\end{todo}
%
\paragraph{Links to resurgence}
%
The examples we study all involve {\em resurgent functions} in the position domain. \begin{todo}[Say a tiny bit about what resurgence does or is good for.]\end{todo} The theory of resurgence has been applied extensively to linear ODEs \cite{loday1994stokes,diverg-resurg--ii}, and it has yielded results about non-linear ODEs as well~\cite{costin-PI,costin_kruskal,diverg-resurg-iii,schiappa-PI}. Geometric arguments show that when a thimble integral has a holomorphic Morse function in the exponent, as we have in at least some of our examples, the corresponding function on the position domain is always resurgent~\cite{Maxim_slide_ERC}\cite[Section 6.2]{kontsevich2022analyticity}. Conjecturally, this property extends to more general thimble integrals---perhaps even infinite-dimensional ones \cite[examples~5--6]{Maxim_slide_ERC}. The linear ODEs and $1$-dimensional thimble integrals that we study provide toy examples of how resurgent functions arise and behave. \begin{revised}As a concrete example, in Section~\ref{resurgence-AL}, we use resurgence to find the Stokes constants of the Airy--Lucas equations.\end{revised}
%
\subsection{Organization of the paper}\label{sec:org}
%
In Section~\ref{sec:historical-context}, we contextualize our work by reviewing some classical results related to Borel regularity. These results come from the literature on asymptotics, ODEs, and integrals over Lefschetz thimbles.

@@

%%\newcommand{\pathdis}{1.5625}
%%\newcommand{\pathoffset}{0.375}
\newcommand{\pathspread}{35}

@@

% the construction lines
\begin{scope}[pwbeige!80!black]
\draw (\peakdis, 0) +(-\phase-\spread-90:1.5*\rshade) -- +(0, 0) -- +(-\phase+\spread+90:1.5*\rshade);
\end{scope}

% the path
\draw[very thick] (\peakdis, 0) +(-\phase-\pathspread-90:\rshade) -- +(0, 0) -- +(-\phase+\pathspread+90:\rshade);
%%\draw[very thick] (-\phase-\pathspread:\pathdis) +(-\phase-\pathspread-90:\rshade) -- +(0, 0) arc (-\phase-\pathspread:-\phase+\pathspread:\pathdis) -- ++(-\phase+\pathspread+90:\rshade);

% coordinate label
\node[anchor=north west, inner sep=2mm] at (-\rfiber, \rfiber) {$z$};
\end{fiber}
\end{tikzpicture}
\captionof{figure}{The thick, black line is the path $\mathcal{C}$.}\label{fig:ref-path}
\end{center}
\begin{old}Parameterize $\mathcal{C}$ using the arc length parameter $t$ which is zero at the midpoint of the circular arc part of $\mathcal{C}$.\end{old} \begin{revised}The path $\mathcal{C}$ is made of two rays, which meet at an angle of $\pi - \Theta + \varepsilon/2$. Parameterize it using the arc length parameter $t$ which is zero where the rays meet. Along $\mathcal{C}$, the distance $\Delta$ to the boundary of $\widehat{\Omega}_\alpha^\Lambda$ satisfies the estimate
\[ \Delta \ge \sin(\varepsilon/2)\,|t|\,. \]
On $\Omega_\alpha^\varepsilon \times \mathcal{C}$, we have
\[ \Re(z\zeta_\alpha) \le |\zeta_\alpha| \big(\Lambda' - \sin(\varepsilon/2)\,|t|\big)\,. \]
\begin{todo}[Justify bound and add pictures.]\end{todo}\end{revised}

@@

\phi \ast_{\zeta_\alpha,0} \psi &= \int_{\substack{\mathcal{S}(\zeta_\alpha) \times \mathcal{S}'(\zeta_\alpha) \\ \zeta_\alpha(a) + \zeta(a') = \zeta_\alpha}} \phi(a)\,\psi(a')\,d\zeta_\alpha(a)\\

@@

First, we show that the convolution product $\phi \ast_{\zeta_\alpha,0} \psi$ is in the domain of the Laplace transform $\laplace_{\zeta_\alpha,0}$. It is uniformly of exponential type $c'' := \max\{c, c'\}$, because

@@

@@

     Notice that the convolution product can be rewritten by introducing the coordinates $\eta(a)=\zeta(a)-\beta$ and $\eta(a')=\zeta(a')+\beta$

@@

       &=\int_{\substack{\mathcal{S}(\eta) \times \mathcal{S}'(\eta) \\ \eta(a) + \eta(a') = \zeta}} \phi(a)\,\psi(a')\,d\eta(a)\,,
   where $\mathcal{S}(\eta)$ is the line segment from $\eta(a)=\alpha$ to $\eta(a)=\zeta_\beta$ and simlarly, $\mathcal{S}'(\eta)$ is the line segment from $\eta(a')=\zeta_\alpha$ to $\eta(a')=\beta$. The coordinate $\eta$ would simplify the computations by showing the dependence on the base point of the Laplace transforms $\laplace_{\zeta,\alpha}[\phi]$ and $\laplace_{\zeta,\beta}[\psi]$.

@@

       &=\int_{\substack{\mathcal{S}(\eta) \times \mathcal{S}'(\eta) \\ \eta(a) + \eta(a') = \zeta}} \phi(a)\,\psi(a')\,d\eta(a)\\

@@

   \begin{todo}[\textbf{A} Does this expression change when $\theta \neq 0$?]\end{todo} where $\eta(a)=(1-s)\alpha+s\zeta_\beta$ and consequently $\eta(a')=\beta s+(1-s)\zeta_\alpha$. Then, the Laplace transform of $\phi \ast_{\zeta, \alpha} \psi$ reads

@@

       &=e^{-z(\alpha+\beta)}\int_{\mathcal{J}_{\zeta_{\alpha+\beta},0}}d\zeta_{\alpha+\beta}\,e^{-z\zeta_{\alpha+\beta}}\zeta_{\alpha+\beta}\, \int_0^1 \phi(a) \psi(a')\,ds \\
       &=e^{-z(\alpha+\beta)}\int_{\mathcal{J}_{\zeta_{\alpha+\beta},0}}d\zeta_{\alpha+\beta}\, \int_0^1 \zeta_{\alpha+\beta}\,e^{-z(1-s)\zeta_{\alpha+\beta}} e^{-z s\zeta_{\alpha+\beta}} \phi(a) \psi(a')\,ds 

@@

        &=\int_0^1 ds\,\int_{\mathcal{J}_{\eta,\beta}}\frac{d\eta(a')}{(1-s)^2}\,e^{-z\eta(a')} (\eta(a')-\beta) e^{-z( (\eta(a')-\beta) \frac{s}{1-s}+\alpha)} \phi(a) \psi(a')\,,
   where in the second step we use $d\zeta_{\alpha+\beta}=d\zeta_\alpha=\frac{d\eta(a')}{1-s}$ and $\zeta_{\alpha+\beta}=\frac{\eta(a')-\beta}{1-s}$. Then, exchanging one more time the order of integration we get
        &=\int_{\mathcal{J}_{\eta,\beta}}d\eta(a') \,e^{-z\eta(a')}  \psi(a') \,\int_0^1 ds\,\frac{\eta(a')-\beta}{(1-s)^2}e^{-z((\eta(a')-\beta) \frac{s}{1-s}+\alpha)} \phi(a)\\
        &=\int_{\mathcal{J}_{\eta,\beta}}d\eta(a') \,e^{-z\eta(a')}  \psi(a') \,\int_{\mathcal{J}_{\eta,\alpha}} d\eta(a)\, e^{-z\eta(a)} \phi(a)\\
   where on the integration path we have $\eta(a)=(\eta(a')-\beta)\frac{s}{1-s}+\alpha$ which mooves along the ray $\mathcal{J}_{\eta,\alpha}$ as $s$ varies in $[0,1]$.   

@@

where $a$ is a preimage of $\zeta = \alpha$ under the map $\zeta = 2i\omega \operatorname{sd}\big(u, \tfrac{1}{\sqrt{2}}\big)$. \begin{todo}[Show thimble picture.]\end{todo} Since exponent is doubly periodic, with period lattice $L = \tfrac{1}{\sqrt{2}}\Z + i\Z$, we can take the thimble to be a real submanifold of the torus $\C / L$.

@@

\begin{todo}[Explain how symmetry of thimble gives $v_\text{uni}$ under thimble projection formula.]\end{todo}

>>>>

Once we know $\iota_a$, we can go through the steps of the Borel regularization process and show that we end up with the same function we started with.
\begin{theorem}[also \ref{thm:maxim-proof}]\label{thm:maxim}
If the integral defining $I_a$ is absolutely convergent, then $I_a$ is Borel regular. More explicitly:
\begin{enumerate}
\item\label{part-1} The function $I_a$ has an asymptotic expansion $\series{I}_a \defeq \aexp^\theta I_a$, which lies in the space $e^{-z \alpha} z^{-1/2} \C\llbracket z^{-1}\rrbracket$. Here, $\theta$ is the direction of the ray $\mathcal{J}^\theta_{\zeta, \alpha}$ that defines the thimble.
\item\label{part-2} The Borel transform $\series{\iota}_a \defeq \borel_\zeta \series{I}_a$ converges near $\zeta = \alpha$.
\item\label{part-3} The sum of $\series{\iota}_a$ can be analytically continued along the ray $\mathcal{J}_{\zeta, \alpha}^\theta$. Its Laplace transform along that ray is well-defined, and equal to $I_a$.
\end{enumerate}
\end{theorem}
For one-dimensional thimbles, this result confirms the expectation that evaluating a thimble integral should be equivalent to taking the Borel sum of its asymptotic series~\cite[Section~2]{dunne-unsal}. Confirming this expectation in higher dimensions would be an interesting topic for future work, since our argument may not generalize straightforwardly.

As an alternative to our argument, Theorem~\ref{thm:maxim} could be deduced from Nevanlinna's theorem~\cite{nevanlinna}. However, that would require a careful asymptotic analysis of $I_a$: one would have to show that its asymptotic series is $1$-Gevrey and uniformly asymptotic to it on a large enough sector. We avoid this asymptotic analysis by working in the position domain and recasting $I_a$ as a Laplace transform integral.
%
\subsubsection{Other results}\label{sec:other_results}
%
\paragraph{New perspectives on the Laplace transform}
%
For Borel summation to work as described in Theorems~\ref{thm:soln_is_Borel_sum} and~\ref{thm:maxim}, one usually needs to take the Laplace and Borel transforms using a particular position coordinate and integration base point. To explain this aspect of Borel regularity, we introduce a geometric picture of the Laplace and Borel transforms, generalizing the position domain from the complex plane to a translation surface $B$. Each translation chart $\zeta$ gives a different version of the Laplace transform, whose associated frequency domain is the cotangent space $T^*_{\zeta = 0} B$. The frequency coordinate $z$ is a canonical coordinate on $T^*_{\zeta = 0}B$, or on $T^*_{\zeta = 0}B^{\otimes n}$ if $\zeta = 0$ is a singularity with cone angle $2\pi n$. The details of this picture are discussed in Sections \ref{sec:geometry_laplace} and \ref{sec:geometry_borel}.
\begin{center}
\phaseSpaceLaplace
\captionof{figure}{The frequency coordinate $z$ on the cotangent spaces of an ordinary point and a singular point. The singularity shown here has cone angle $6\pi$, like the singularities of the translation surface associated with the Airy function.}
\end{center}

@@

In the literature on Borel summation, the Airy equation has been discussed many times, using different approaches and conventions. In Section~\ref{airy-comparison}, we explain how the treatments in \cite[Section 2.2]{lectures-Marino}, \cite[Section 6.14]{diverg-resurg-i}, and \cite[Section 2.2]{kawai-takei} line up with ours.
 \begin{todo}Other treatments of the anharmonic oscillator: \cite{bender-wu}\cite[Appendix B]{aniceto2019primer}\cite[Section 2.5.3]{sternin1995borel}).\end{todo}
%
\paragraph{Links to resurgence}
%
The examples we study all involve {\em resurgent functions} in the position domain. \begin{draft}
    The theory of resurgence introduced by \'Ecalle~\cite{EcalleI,EcalleII,EcalleIII}
\end{draft} \begin{todo}[Say a tiny bit about what resurgence does or is good for.]\end{todo} The theory of resurgence has been applied extensively to linear ODEs \cite{loday1994stokes,diverg-resurg--ii}, and it has yielded results about non-linear ODEs as well~\cite{costin-PI,costin_kruskal,diverg-resurg-iii,schiappa-PI}. Geometric arguments show that when a thimble integral has a holomorphic Morse function in the exponent, as we have in at least some of our examples, the corresponding function on the position domain is always resurgent~\cite{Maxim_slide_ERC}\cite[Section 6.2]{kontsevich2022analyticity}. Conjecturally, this property extends to more general thimble integrals---perhaps even infinite-dimensional ones \cite[examples~5--6]{Maxim_slide_ERC}. The linear ODEs and $1$-dimensional thimble integrals that we study provide toy examples of how resurgent functions arise and behave. \begin{revised}As a concrete example, in Section~\ref{resurgence-AL}, we use resurgence to find the Stokes constants of the Airy--Lucas equations.\end{revised}
%
\subsection{Organization of the paper}\label{sec:org}
%
In Section~\ref{sec:historical-context}, we contextualize our work by reviewing some classical results related to Borel regularity. These results come from the literature on asymptotics, ODEs, and integrals over Lefschetz thimbles.

@@

\newcommand{\pathspread}{35}
\newcommand{\angmarkrad}{1}
\newcommand{\distmarkrad}{2.5}
\pgfmathsetmacro{\bdrydist}{\distmarkrad*sin(\pathspread-\spread)}

@@

% the construction lines
\begin{scope}[pwbeige!80!black]
\draw (\peakdis, 0) +(-\phase-\spread-90:1.5*\rshade) -- +(0, 0) -- +(-\phase+\spread+90:1.5*\rshade);
\draw[shorten <=0.3mm, shorten >=0.4mm] (\peakdis, 0) ++(\phase+\spread+90:\angmarkrad) arc[start angle=\phase+\spread+90, delta angle=\pathspread-\spread, radius=\angmarkrad] node [midway, circle, inner sep=1, anchor=-90+0.5*\spread+0.5*\pathspread)] {$\tfrac{\varepsilon}{2}$};
%%\draw (\peakdis, 0) ++(-\phase-\spread-90:\angmarkrad) arc [start angle=\phase-\spread-90, delta angle=\spread-\pathspread, radius=\angmarkrad] node[midway, circle, inner sep=1, anchor=90-0.5*\spread-0.5*\pathspread] {$\tfrac{\varepsilon}{2}$};
\draw[shorten >=0.3mm] (\peakdis, 0) ++(\phase+\pathspread+90:\distmarkrad) -- ++(\phase+\spread:\bdrydist) node[midway, circle, inner sep=0, anchor=-90+\spread] {$t \sin(\tfrac{\varepsilon}{2})$};
\end{scope}

% the path
\draw[very thick] (\peakdis, 0) +(-\phase-\pathspread-90:\rshade) -- +(0, 0) -- +(-\phase+\pathspread+90:\rshade);
\draw (\peakdis, 0) ++(\phase+\pathspread+90:0.5*\distmarkrad) node[anchor=180+\pathspread] {$t$};
\draw (\peakdis, 0) ++(\phase+\pathspread+90:\distmarkrad) +(\pathspread:1mm) -- +(180+\pathspread:1mm);

% coordinate label
\node[anchor=north west, inner sep=2mm] at (-\rfiber, \rfiber) {$z$};
\end{fiber}
\end{tikzpicture}
\captionof{figure}{The thick black line is the path $\mathcal{C}$.}\label{fig:ref-path}
\end{center}
\begin{old}Parameterize $\mathcal{C}$ using the arc length parameter $t$ which is zero at the midpoint of the circular arc part of $\mathcal{C}$.\end{old} \begin{revised}The path $\mathcal{C}$ is made of two rays, which meet at an angle of $\pi - \Theta + \varepsilon$. Parameterize it using the arc length parameter $t$ which is zero where the rays meet. Along $\mathcal{C}$, the distance $\Delta$ to the boundary of $\widehat{\Omega}_\alpha^\Lambda$ satisfies the estimate
\[ \Delta \ge \sin(\varepsilon/2)\,|t|\,, \]
as shown in Figure~\ref{fig:ref-path}. On $\Omega_\alpha^\varepsilon \times \mathcal{C}$, we have
\[ \Re(z\zeta_\alpha) \le |\zeta_\alpha| \big(\Lambda' - \sin(\varepsilon/2)\,|t|\big)\,. \]
\begin{todo}[Justify bound and add pictures.]\end{todo}\end{revised}

@@

\phi \ast_{\zeta_\alpha,0} \psi &= \int_{\substack{\mathcal{S}(\zeta_\alpha) \times \mathcal{S}'(\zeta_\alpha) \\ \zeta_\alpha(a) + \zeta_\alpha(a') = \zeta_\alpha}} \phi(a)\,\psi(a')\,d\zeta_\alpha(a)\\

@@

First, we show that the convolution product $\phi \ast_{\zeta_\alpha,0} \psi$ is in the domain of the Laplace transform $\laplace_{\zeta_\alpha,0}$. \begin{todo}[Right now, we're only assuming that $\phi$ and $\psi$ have well-defined Laplace transforms, which doesn't imply that they're uniformly of exponential type]\end{todo} It is uniformly of exponential type $c'' := \max\{c, c'\}$, because

@@

   by exchanging the order of integration we find \begin{todo}[recalling that $\zeta_\alpha(a') = (1-s)\zeta_\alpha$ on the integration path that defines the convolution]\end{todo}

@@

The convolution product can be rewritten by introducing the coordinates $\zeta_\beta$ and $\zeta_{-\beta}$:

@@

&=\int_{\substack{\mathcal{S}(\zeta_{\beta}) \times \mathcal{S}'(\zeta_{-\beta}) \\ \zeta_{\beta}(a) + \zeta_{-\beta}(a') = \zeta}} \phi(a)\,\psi(a')\,d\zeta(a)\,,
where $\mathcal{S}(\zeta_{\beta})$ is the line segment from $\zeta_\beta(a)=\alpha$ to $\zeta_\beta(a)=\zeta_\beta$ and simlarly, $\mathcal{S}'(\zeta_{-\beta})$ is the line segment from $\zeta_{-\beta}(a')=\zeta_\alpha$ to $\zeta_{-\beta}(a')=\beta$. This change of coordinates simplifies our computations by showing how the convolution product depends on the base points of the Laplace transforms $\laplace_{\zeta,\alpha}[\phi]$ and $\laplace_{\zeta,\beta}[\psi]$.

@@

    &=\int_{\substack{\mathcal{S}(\zeta_\beta) \times \mathcal{S}'(\zeta_{-\beta}) \\ \zeta_\beta(a) + \zeta_{-\beta}(a') = \zeta}} \phi(a)\,\psi(a')\,d\zeta(a)\\

@@

\begin{todo}[\textbf{A} Does this expression change when $\theta \neq 0$?]\end{todo} where $\zeta_\beta(a)=(1-s)\alpha+s\zeta_\beta$ and consequently $\zeta_{-\beta}(a')=\beta s+(1-s)\zeta_\alpha$. Then, the Laplace transform of $\phi \ast_{\zeta, \alpha} \psi$ reads

@@

    &=e^{-z(\alpha+\beta)}\int_{\mathcal{J}_{\zeta_{\alpha+\beta},0}}d\zeta_{\alpha+\beta}\,e^{-z\zeta_{\alpha+\beta}}\zeta_{\alpha+\beta}\, \int_0^1 \phi(a)\,\psi(a')\,ds \\
    &=e^{-z(\alpha+\beta)}\int_{\mathcal{J}_{\zeta_{\alpha+\beta},0}}d\zeta_{\alpha+\beta}\, \int_0^1 \zeta_{\alpha+\beta}\,e^{-z(1-s)\zeta_{\alpha+\beta}} e^{-z s\zeta_{\alpha+\beta}} \phi(a)\, \psi(a')\,ds\,.
By exchanging the order of integration we find 

@@

        &=\int_0^1 ds\,\int_{\mathcal{J}_{\zeta,\beta}}\frac{d\zeta(a')}{(1-s)^2}\,e^{-z\zeta_{-\beta}(a')} (\zeta_{-\beta}(a')-\beta) e^{-z( (\zeta_{-\beta}(a')-\beta) \frac{s}{1-s}+\alpha)} \phi(a) \psi(a')\,,
   where in the second step we use $d\zeta_{\alpha+\beta}=d\zeta_\alpha=\frac{d\zeta_{-\beta}(a')}{1-s}$ and $\zeta_{\alpha+\beta}=\frac{\zeta_{-\beta}(a')-\beta}{1-s}$ \begin{todo}[this comes from the expression for $\zeta_{-\beta}(a')$ above, by subtracting $\beta$ from both sides and then rearranging]\end{todo}. Then, exchanging one more time the order of integration we get
        &=\int_{\mathcal{J}_{\eta,\beta}}d\zeta(a') \,e^{-z\zeta_{-\beta}(a')}  \psi(a') \,\int_0^1 ds\,\frac{\zeta_{-\beta}(a')-\beta}{(1-s)^2}e^{-z((\zeta_{-\beta}(a')-\beta) \frac{s}{1-s}+\alpha)} \phi(a)\\
        &=\int_{\mathcal{J}_{\zeta,\beta}}d\zeta(a') \,e^{-z\zeta_{-\beta}(a')}  \psi(a') \,\int_{\mathcal{J}_{\zeta,\alpha}} d\zeta(a)\, e^{-z\zeta_\beta(a)} \phi(a)\\
         &=\int_{\mathcal{J}_{\zeta,\beta}}d\zeta(a') \,e^{-z\zeta(a')}  \psi(a') \,\int_{\mathcal{J}_{\zeta,\alpha}} d\zeta(a)\, e^{-z\zeta(a)} \phi(a)
   where on the integration path we have $\zeta(a)=(\zeta_{-\beta}(a')-\beta)\frac{s}{1-s}+\alpha$ which mooves along the ray $\mathcal{J}_{\zeta,\alpha}$ as $s$ varies in $[0,1]$.   

@@

where $a$ is a preimage of $\zeta = \alpha$ under the map $\zeta = 2i\omega \operatorname{sd}\big(u, \tfrac{1}{\sqrt{2}}\big)$. \begin{todo}[\textbf{A} Show thimble picture.]\end{todo} Since exponent is doubly periodic, with period lattice $L = \tfrac{1}{\sqrt{2}}\Z + i\Z$, we can take the thimble to be a real submanifold of the torus $\C / L$.

@@

\begin{todo}[Note that this presents $V_\alpha$ as the Laplace transform of $v_\text{uni}$.]\end{todo} \begin{todo}[Explain how symmetry of thimble gives $v_\text{uni}$ under thimble projection formula.]\end{todo}
